---
title: "Introduction to assetr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to assetr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(assetr)
```

# Simplifying Stock and Asset Analysis in R
The `assetr` package is a powerful tool designed for stock and asset analysis in R. While still in its early stages of development, `assetr` aims to become an essential extension of existing packages, providing a simplified and intuitive approach to analysing stocks and assets.

## Key Features
- **Streamlined Analysis**: assetr aims to streamline the analysis process, making it easier for both beginners and experienced users to perform comprehensive stock and asset analysis in R.

- **Simplification of Existing Packages**: assetr builds upon existing packages and simplifies their functionality, allowing users to perform complex tasks with fewer lines of code.

- **Datasets for screening**: assetr includes a wide range of datasets that are essential for comprehensive screening and analysis.


## Getting Started
To start using assetr, simply install the package from CRAN using the install.packages("assetr") command. Once installed, load the package into your R session with the library(assetr) command.

## Package Dependencies
